---
title: "SCIP_mturk-study1B_analysis"
author: "Pooja Paul"
date: "12/9/2019"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r opts, include=FALSE, echo = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = TRUE)

# edited line below to help with saving plots as .png files; 
# knitr::opts_chunk$set(echo = TRUE, dev = c('png', 'pdf'),fig.align = 'center') 
   

```
# Load packages

```{r loadPackages, echo = FALSE, message=FALSE, warning=FALSE}

library(here)
library(langcog)   #install.packages("devtools"); devtools::install_github("langcog/langcog")
library(Hmisc) # --- could use this for alt. bootstrapping fns

# added 9-27-19 - I
library(stringr) #processing strings
library(compute.es) #for calculating effect sizes
library(lme4) 
#library(regex) 

#added 9-27-19 - II
# install.packages(c("skimr", "visdat", "summarytools", "DT"))
library(skimr)
library(visdat)
# library(summarytools)  # must have XQuartz installed 
# getting following error: package ‘summarytools’ was built under R version 3.5.2 couldn't connect to display ":0"system has no X11 capabilities, therefore only ascii graphs will be produced by dfSummary()
library(DT)
library(tidyverse)  #note: contains ggplot2, dplyr, tidyr
library(car)
library(lme4)

```

# Structure data

Steps in data processing pipeline:

(1) Load csv file containing raw ON/OFF data (Qualtrics 'Hot Spots' Question type) 
    -- Note: no timing info included in this datafile.

```{r tidyUp, echo = FALSE, message=FALSE, warning=FALSE}
files <- dir(here("SCIP_1B_data_ANON"), "*.csv")
d <- tibble(fname = files) %>%
  mutate(id = c(1,10,11,12,2,3,4,9,13,14,15,16,5,6,7,8)) %>% # adds index to keep track of data frames
  arrange(id) %>% # arranges in ascending list order
  select(id, fname) %>% 
  split(.$id) %>% # splits into list of data frames
  map_df(function (x) {  # defines function to run on each data frame
    read_csv(here("SCIP_1B_data_ANON", x$fname)) %>% 
      select(ends_with("_1"), -contains("timing")) %>% 
      mutate(listNum = x$id, 
             subid = str_c(as.character(listNum), '-', as.character(1:n()))) %>%
  pivot_longer(names_to = "trial", 
               values_to = "response", cols = c(-listNum, -subid)) %>%
  separate(trial, sep = "-", into = c("trialName", "jars")) %>% 
  mutate(response = ifelse(response=="On", 
                           "left",ifelse(response=="Off","right","NA"))) %>% 
  mutate(trialType = "critical",
         trialType = ifelse(str_detect(trialName, "G"), "gen", trialType),
         trialType = ifelse(str_detect(trialName, "R"), "recap", trialType)) %>%
  mutate(trialName = str_replace(trialName, ":purple",""),
         jars = str_replace(str_replace(jars, "_1", ""), "white", "PW")) })

```


Merge in key information and score trials
```{r echo = FALSE, message=FALSE, warning=FALSE}
keys <- read_csv("SCIP_1B_key_full.csv") 

#TODO: missing some Cr 'correctSide' values in later lists --- fix 
d <- left_join(d, keys) %>%
  mutate(acc = ifelse(response==correctSide,1,0))


```

Aggregate and plot. 

```{r fullData}
#grouping by trial type (Critical/Generalization/Recap)
ms <- d %>%   
  group_by(trialType, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

# plot #1
ggplot(ms, aes(x = trialType, y = mean, fill = trialType)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 1: Performance per trial type across lists") +
  geom_hline(yintercept = .5, lty = 3)


#grouping by trial name (n = 8)
ms <- d %>%   
  group_by(trialName,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)
view(ms)
# plot #1 (barplot)
ggplot(ms, aes(x = trialName, y = mean, fill = trialName)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 2a: Performance by trial across lists") +
  geom_hline(yintercept = .5, lty = 3)

# plot #2 (boxplot)
ms <- d %>%   
  group_by(trialName, listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)
view(ms)
ggplot(ms, aes(x = trialName, y = mean, fill = trialName)) + 
  geom_boxplot() +
  theme(legend.position = "none") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 2b: Performance per trial across lists (boxplot)") +
  geom_hline(yintercept = .5, lty = 3)

```
```{r byFamOrder}
# df with just INCREASING fam order (odd-numbered lists)
ms_increasing <- d %>% 
  filter(listNum %in% c(1,3,5,7,9,11,13,15)) %>% 
  #group_by(trialType, id) %>%
  group_by(trialName, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)
#ggplot(ms_increasing, aes(x = trialType, y = mean, fill = trialType)) + 
ggplot(ms_increasing, aes(x = trialName, y = mean, fill = trialName)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 3: Performance by trial (INCREASING fam order)") +
  geom_hline(yintercept = .5, lty = 3)

# df with just DECREASING fam order (even-numbered lists)
ms_decreasing <- d %>% 
  filter(listNum %in% c(2,4,6,8,10,12,14,16)) %>% 
  #group_by(trialType, id) %>%
  group_by(trialName, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)
#ggplot(ms_decreasing, aes(x = trialType, y = mean, fill = trialType)) + 
ggplot(ms_decreasing, aes(x = trialName, y = mean, fill = trialName)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 4: Performance by trial (DECREASING fam order)") +
  geom_hline(yintercept = .5, lty = 3)
```
```{r dataByList}
#aggregate performance grouping by list
ms.byList <- d %>%   
  group_by(listNum,trialType, add = FALSE) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)
ggplot(ms.byList, aes(x = listNum, y = mean, fill = listNum)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 5: Overall accuracy by list") +
  geom_hline(yintercept = .5, lty = 3)


#grouping by trial type 
ms.typeByList <- d %>%   
  select(subid,listNum,trialType,trialName,acc) %>% 
  group_by(listNum,trialType,subid) %>% 
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE) %>% 
  ungroup()
view(ms.typeByList)
# plot #1 (doesn't make sense stacked, needed to be grouped/clustered)
ggplot(ms.typeByList, aes(x = listNum, y = mean, fill = trialType)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 6a: Accuracy by list by trial type (stacked)") +
  geom_hline(yintercept = 1.5, lty = 3) 
# plot#2
ggplot(ms.typeByList, aes(x = listNum, y = mean, fill = trialType)) + 
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  geom_hline(yintercept = .5, lty = 3) +
  ggtitle("Figure 6b: Accuracy by list per trial type (boxplot)") +
  facet_wrap(~trialType)

```

Trying to figure out what's going on with R3 performance (performance across lists is at chance):
```{r investigatingR3}
ms_R3 <- d %>% 
  filter(trialName == "R3") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_R3, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 8a: Accuracy by list for Recap 3") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for R2 by list: 
```{r investigatingR2}
ms_R2 <- d %>% 
  filter(trialName == "R2") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_R2, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 8b: Accuracy by list for Recap 2") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for R1 by list: 
```{r investigatingR1}
ms_R1 <- d %>% 
  filter(trialName == "R1") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_R1, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 8c: Accuracy by list for Recap 1") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for R4 by list: 
```{r investigatingR4}
ms_R4 <- d %>% 
  filter(trialName == "R4") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_R4, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 8d: Accuracy by list for Recap 4") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for R1 thru R4 (aggregated) by list: 
```{r investigatingRecaps}
ms_R1234 <- d %>% 
  filter(trialName %in% c('R1','R2','R3','R4'))%>% 
  group_by(listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_R1234, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 8e: Accuracy by list for Recaps 1-4") +
  geom_hline(yintercept = .5, lty = 3)
```


cf. performance for G1 by list: 
```{r investigatingG1}
ms_G1 <- d %>% 
  filter(trialName == "G1") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_G1, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 9a: Accuracy by list for Generalization 1") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for G2 by list: 
```{r investigatingG2}
ms_G2 <- d %>% 
  filter(trialName == "G2") %>% 
  group_by(listNum, subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_G2, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 9b: Accuracy by list for Generalization 2") +
  geom_hline(yintercept = .5, lty = 3)
```

cf. performance for G1+ G2 (aggregated) by list: 
```{r investigatingGens}
ms_G12 <- d %>% 
  filter(trialName %in% c('G1','G2'))%>% 
  group_by(listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_G12, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 9c: Accuracy by list for Generalizations 1+2") +
  geom_hline(yintercept = .5, lty = 3)
```


cf. performance for Critical Trials (aggregated) by list: 
```{r investigatingCrACrB}
ms_CrAB <- d %>% 
  filter(trialName %in% c('CrA','CrB'))%>% 
  group_by(listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_CrAB, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 10a: Accuracy by list for Critical trials (CrA/CrB)") +
  geom_hline(yintercept = .5, lty = 3)
```
cf. performance for CrA (2(Left)vs.4(Right)) Trials by list: 
```{r investigatingCrA}
ms_CrA <- d %>% 
  filter(trialName == 'CrA')%>% 
  group_by(listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_CrA, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 10b: Accuracy by list for Critical trial A (CrA)") +
  geom_hline(yintercept = .5, lty = 3)
```
cf. performance for CrB (4(Left)vs.2(Right)) Trials by list: 
```{r investigatingCrB}
ms_CrB <- d %>% 
  filter(trialName == 'CrB')%>% 
  group_by(listNum,subid) %>%
  summarise(acc = mean(acc, na.rm=TRUE)) %>%
  multi_boot_standard(col = "acc", na.rm = TRUE)

ggplot(ms_CrB, aes(x = listNum, y = mean, fill = listNum)) +  
  geom_bar(stat = "identity") +
  geom_linerange(aes(ymin = ci_lower, ymax = ci_upper)) + 
  ggtitle("Figure 10c: Accuracy by list for Critical trials (CrB)") +
  geom_hline(yintercept = .5, lty = 3)
```


