---
title: "SCIP-mturk_study1a-analysis_2019"
author: "Pooja Paul"
date: "9/24/2019"
output:
  html_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE, echo = FALSE, cache = FALSE}
#knitr::opts_chunk$set(echo = TRUE)

# edited line below to help with saving plots as .png files; 
knitr::opts_chunk$set(echo = TRUE, dev = c('png', 'pdf'),fig.align = 'center') 
   
```
# Load packages

```{r loadPackages, message=FALSE, warning=FALSE}

library(here)
library(langcog)   #install.packages("devtools"); devtools::install_github("langcog/langcog")
library(Hmisc) # --- could use this for alt. bootstrapping fns

# added 9-27-19 - I
library(stringr) #processing strings
library(compute.es) #for calculating effect sizes
library(lme4) 
#library(regex) 

#added 9-27-19 - II
# install.packages(c("skimr", "visdat", "summarytools", "DT"))
library(skimr)
library(visdat)
library(summarytools)  # must have XQuartz installed 
# getting following error: package ‘summarytools’ was built under R version 3.5.2 couldn't connect to display ":0"system has no X11 capabilities, therefore only ascii graphs will be produced by dfSummary()
library(DT)
library(tidyverse)  #note: contains ggplot2, dplyr, tidyr
library(car)
library(lme4)

```

# Structure data

Steps in data processing pipeline:

(1) Load csv file containing raw ON/OFF data (Qualtrics 'Hot Spots' Question type) 
    -- Note: no timing info included in this datafile.

```{r loadData}
# STEP 1 #
rawData_wide <- read_csv(here::here("SCIP_adult_study1a_acc-rawData.csv"))
head(rawData_wide)
```

(2) Tidy up data, by:
      (a) selecting just the columns we need:subjectNum + ON/OFF responses for 8 test trials
      (b) mapping ON/OFF responses to correct/chosen/acc data
      (c) additional filtering
      

```{r tidyingUp}
#(a) selecting subset of columns needed for calculating accuracy per trial
# # Use this to positively select req. cols if working directly off qualtrics output csv with many extraneous cols:
cleanData_wide = rawData_wide %>% 
  select(subjectNum,ends_with("_1")) %>% 
  mutate(G2_correct = "left", R3_correct = "right",
         R2_correct = "right", CrB_correct = "left",
         R1_correct = "right", G1_correct = "left",
         CrA_correct = "right", R4_correct = "left") %>%   
  mutate(subjectNum = factor(subjectNum))  
#replace '-' with '_', etc.
  colnames(cleanData_wide) <- colnames(cleanData_wide) %>% 
    str_replace("-", "_") %>% 
    str_replace("_.._1","_chosen")

  df.long <- cleanData_wide %>% 
  gather(trial, value, -subjectNum) %>% 
   arrange(subjectNum,trial) %>% 
   separate(trial, into = c("trial", "variable")) %>% 
   spread(variable, value) %>% 
   mutate(chosen = ifelse(chosen =="On","left","right")) %>% 
   mutate(acc = ifelse(chosen==correct,1,0)) %>% 
   mutate(blockNum = ifelse(trial %in% c("G2","R3","R2","CrB"),1,2)) 
  
# add trialType info (recap, crit, gen)
  # credit: Tobias Gerstenberg
longData = df.long %>% 
  mutate(trialType = "critical",
         trialType = ifelse(str_detect(trial, "G"), "gen", trialType),
         trialType = ifelse(str_detect(trial, "R"), "recap", trialType))

# saving tidied up data in long form:
#write.csv(longData,file="SCIP-MT-study1a_acc-cleanData_long.csv")

```

ALT code snippet from MCF: 

```{r MCF-code, eval=FALSE}
d <- read_csv(here::here("SCIP_adult_study1a_acc-rawData.csv")) %>%
  mutate(G2_correct = "left",
         R3_correct = "right",
         R2_correct = "right",
         CrB_correct = "left",
         R1_correct = "right", 
         G1_correct = "left",
         CrA_correct = "right",
         R4_correct = "left") %>%
  select(-contains("_2")) %>% # drop _2 as that's the right side
  gather(variable, value, `G2-PG_1`:R4_correct) %>%    
  mutate(variable = str_replace(variable, "-", "_")) %>% # deal with naming issue
  separate(variable, into = c("trial", "variable")) %>%
  mutate(variable = ifelse(variable == "correct", "correct", "chosen")) %>%
  spread(variable, value) %>%
  mutate(chosen = ifelse(chosen=="On", "left", "right")) %>%
  mutate(acc = chosen == correct) %>% 
  mutate(blockNum = ifelse(trial %in% c("G2","R3","R2","CrB"),1,2))

```


# Plots 

## (A) Performance across 8 trials

- aggregating over participants with bootstrapped CIs

```{r visualization}

ms <- longData %>%
  group_by(trial, subjectNum) %>%
  summarise(acc = mean(acc)) %>%
  multi_boot_standard(col = "acc") %>% 
  mutate(colorindex = str_sub(trial, end = -2), #??
         colorindex = factor(colorindex,
                             levels = c("Cr", "G", "R"),
                             labels = c("critical", "generalization", "recap")))

ggplot(ms, aes(x = trial, y = mean, fill = colorindex)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  shape = 21,  # fillable circles 
                  size = 1) + 
  geom_hline(yintercept = .5, lty = 2) +
  labs(fill = "Trial Type",
       x = "Trial",
       y = "Proportion Correct") + 
  ylim(0, 1) + 
  theme_classic() + 
  scale_fill_brewer(palette = "Set1") + 
  theme(text = element_text(size = 20))

#ggsave("SCIP1a_acc-by-trial.png")

```
 
 
## (B) Performance by trial type 
 
- critical vs. generalization vs. recap
  
```{r}
 by_trial.type <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1)) %>% 
  group_by(type, subjectNum) %>% 
  summarise(acc = mean(acc)) %>%
  multi_boot_standard(col = "acc") %>% 
  ungroup %>% 
  mutate(type = factor(type, levels = c("C", "G", "R"),
                             labels = c("critical", "generalization", "recap")))
  

ggplot(by_trial.type, aes(x = type, y = mean, fill = type)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  shape = 21,  # fillable circles 
                  size = 1) + 
  geom_hline(yintercept = .5, lty = 2) +
  labs(x = "Trial Type",
       y = "Proportion Correct") + 
  ylim(0,1) + 
  theme_classic() + 
  scale_fill_brewer(palette = "Set1") + 
  theme(text = element_text(size = 20),
        legend.position = "none")

#ggsave("SCIP1a_acc-by-type.png")
  
```
  
## (C) Performance by block (aggregate)
  
  - Block 1 vs. Block 2
  
```{r}
by_block <- longData %>% 
  group_by(blockNum,subjectNum) %>% 
  summarise(acc = mean(acc)) %>% 
  multi_boot_standard(col = "acc") %>% 
  ungroup %>% 
  mutate(blockNum = factor(blockNum, levels = c("1", "2"),
                             labels = c("Block 1", "Block 2")))

ggplot(by_block, aes(x = blockNum, y = mean)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  shape = 21,  # fillable circles 
                  size = 1) + 
  geom_hline(yintercept = .5, lty = 2) +
  labs(x = "Block Number",
       y = "Proportion Correct") + 
  ylim(0,1) + 
  theme_classic() + 
  scale_fill_brewer(palette = "Set1") + 
  theme(text = element_text(size = 20),
        legend.position = "none")

#ggsave("SCIP1a_acc-by-block.png")

```
  
  
## (D) Performance by trial type, separated by block 
  
```{r}
by_type_block <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1)) %>% 
  group_by(blockNum,type,subjectNum) %>% 
  summarise(acc = mean(acc)) %>% 
  multi_boot_standard(col = "acc") %>% 
  ungroup %>% 
  mutate(blockNum = factor(blockNum, levels = c("1", "2"),
                           labels = c("Block 1", "Block 2"))) %>% 
  mutate(type = factor(type, levels = c("C", "G", "R"),
                             labels = c("critical", "generalization", "recap")))

# pretty dot plot 
ggplot(by_type_block, aes(x = blockNum, y = mean, fill = type)) + 
  geom_pointrange(aes(ymin = ci_lower, ymax = ci_upper),
                  shape = 21,  # fillable circles 
                  size = 1,
                  position = "jitter") + 
  geom_hline(yintercept = .5, lty = 2) +
  labs(fill = "Trial Type",
       x = "Block Number",
       y = "Proportion Correct") + 
  ylim(0,1) + 
  theme_classic() + 
  scale_fill_brewer(palette = "Set1") + 
  theme(text = element_text(size = 18))

# boxplot of accuracy as a function of trial type
plot(mean~type, data = by_type_block, xlab = "trial type", ylab = "mean accuracy", main="Accuracy by trial type") 

#ggsave("SCIP1a_boxplot_acc-by-type-by-block.png")


# boxplot of accuracy as a function of block number
plot(mean~blockNum, data = by_type_block, xlab = "block number", ylab = "mean accuracy", main = "Accuracy by block number") 


```
  
## (E) Relationship between performance on recap (R1:R4) vs. critical trials

```{r corr}

by_Cr_R <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1)) %>% 
  filter(type != "G") %>% 
  group_by(subjectNum, type) %>% 
  summarise(acc = mean(acc)) %>% 
  ungroup %>% 
  mutate(type = factor(type, levels = c("C", "R"))) %>% 
  spread(type, acc)

#correlation b/w recap performance and critical trial performance
cor.test(by_Cr_R$C, by_Cr_R$R)

cor(by_Cr_R)
  
```

## (F) Relationship between performance on inner-recap (R2, R3) vs. critical trials
```{r corr-Inner}
# df with critical and inner-recap trial acc per participant
by_Cr_IR <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1)) %>% 
  filter(trial == "R2") %>% 
  filter(trial == "R3") %>%   # I'm sure I can be more efficient here :)
  group_by(subjectNum, type) %>% 
  summarise(acc = mean(acc)) %>% 
  ungroup %>% 
  mutate(type = factor(type, levels = c("C", "R"))) %>% 
  spread(type, acc)

#TODO: plotting critical-trial acc against inner-recap acc
  
#correlation 
cor.test(by_Cr_IR$C, by_Cr_IR$R)

cor(by_Cr_IR)


# Not quite right
  ggplot(by_Cr_IR, aes(x=C, y=R)) +
  geom_point(size=2) +
  geom_smooth(method=lm)

```



## (G) other (TBD)  

```{r, eval=FALSE, include=FALSE, echo=FALSE}

by_subject_type <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1)) %>% 
  group_by(subjectNum, type) %>% 
  summarise(acc = mean(acc)) %>% 
  ungroup %>% 
  mutate(type = factor(type, levels = c("C", "G", "R"),
                             labels = c("critical", "gen", "recap")))


plot(acc~type, data = by_subject_type)  # keep 

```


# Analyses 

## Planned primary analysis:
```{r analysis-1}
data <- longData %>% 
  mutate(type = str_sub(trial, start = 1, end = 1))  %>% 
  mutate(type = factor(type, levels = c("C", "G", "R"))) 

#glmer(acc ~ type + (type | subjectNum), data = data, family = “binomial”)

```

## Planned secondary analyses: 
```{r analysis-2}

```

